Real-Time Certified Probabilistic Pedestrian Forecasting

### 2017-02-16 pedestrian_forecasting_iros_2017.tex
ran through the implementation.

 \subsection{Evaluating Performance}
In this section we establish our methods for evaluating the quality of our predictions, and comparing them against the model from [8] and a random walk.
We implement our model as well as the evaluation code in Python 2.6. 
Our implementation is available online \footnote{https://github.com/OkayHughes/iros2017\_pedestrian\_forecasting}.

@@

	\caption{We behave qualitatively and quantitatively better than kitani in this example. Our algorithm starts out with a dense distribution, which spreads with time, whereas Kitani et al.'s algorithm is very confident in its mistake.}

@@

	\caption{We predict this trajectory very well, and while Kitani et al. captures the same behaviour, however their motion model doesn't adequately keep up with the ground truth of the pedestrian.}

Our data came from the Stanford Drone Dataset in the form of hand annotated bounding boxes around agents (e.g. cars, pedestrians, bicycles). 
Our test data used the bicycle annotations. 
We did a 2-fold cross validation on 4 different scenes of varying complexity. 
Our analysis used the same partitions of the trajectories for all three predictors.

Our data came from the Stanford Drone Dataset, in the form of hand annotated bounding boxes around agents (e.g. cars, pedestrians, bicycles). Our datasets used the bicycle data. We did a 2-fold cross validation on 4 different scenes of varying complexity. Our analysis used the same partitions of the trajectories for all three predictors.

The algorithm provided by Kitani et al. was given additional information when making predictions that neither ours nor the random walk model were provided, namely the endpoint of the test trajectory. Without these data the implementation of the predictor provided by the authors devolves into a random walk.

The output distributions of the three algorithms were compared using their integrals over the cells of a suitably fine regular grid over our domain. These integrals are used to visualize the distributions in Figures \ref{fig:death-1-2} and \ref{fig:bookstore-1-2}.
In keeping with our measurement model, the ground truth compared against was a grid that was identically zero except on a bounding box around the measurement at time $t$. The dimensions of the bounding box were the average bounding box dimensions in the training data set. Because our predictions all share the same scale, we were able to amalgamate all of the prediction and truth values for all of the simulated agents at a given time step and generate ROC curves. Figure \ref{fig:auc_vs_time} shows the Area Under the Curve of these ROC curves versus time.
\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{./figures/the_results.eps}
	\caption{We see that at all times we outperform Random Walk and Kitani et al.'s algorithm. The initial dip in Kitani et al.'s algorithm is due to their initial distribution being very sharp.}
	\label{fig:auc_vs_time}
\end{figure}

Disregarding small time scales where any algorithm will be reasonably accurate, our predictor behaves much better than any of the others at moderately large $t$, where we capture the  behavior of the agent without suffering the misplaced confidence observed in Kitani et al.'s predictions. Their encoding of velocity results in the prediction lagging behind the actual observed motion. Even given significantly better information, Kitani et al. generates lower quality predictions than our algorithm at all time scales. 
\begin{table}
	\begin{center}
		\caption{Runtimes}
		\label{tab:time}
		\renewcommand{\arraystretch}{1.5}% Spread rows out...
		\begin{tabular}{||c | c c  c ||} 
			\hline
			& Our Predictor & Random Walk & Kitani et al. \\ [0.5ex] 
			\hline 
			$\frac{\mathrm{time}}{\mathrm{frame}}$ & 0.0169s & 2.1E-7s & 0.0614s \\
			\hline

		\end{tabular}

	\end{center}
\end{table}

The run time per frame for each algorithm was generated using total run time for 400 frames, averaged across several agents and scenes, divided by the number of frames. This is shown in Table~\ref{tab:time}. Our algorithm implementation leveraged its embarassing parallelism using a relatively naive parallelization scheme, which split the computation of frames among 18 cores. It's highly probable that our run times would significantly decrease using an implementation of our algorithm in C that uses a more clever scheme. Kitani et al. was timed with minimal modification to the source code provided by the authors.

Figure \ref{fig:auc_vs_time} shows that at all time scales our algorithm has better predictive capability than Kitani et. al's. We also run over 3 times faster than their algorithm, at over 60FPS.  Figures \ref{fig:death-1-2} and \ref{fig:bookstore-1-2} show the qualitative superiority of our predictions on several scenes.

>>>>

 \subsection{Evaluating Performance}

This section establishes our methods performance and compares it to the model from \cite{Kitani2012} and a random walk.
We implement our model as well as our evaluation code in Python 2.6. 
Our implementation is available online\footnote{https://github.com/OkayHughes/iros2017\_pedestrian\_forecasting}.
Our test data used the bicycle annotations in \cite{Robicquet2016}. 
We did a 2-fold cross validation on 4 different scenes of varying complexity. 
Our analysis used the same partitions of the trajectories for all three predictors.

	\caption{An illustration of the predictions generated by the various algorithms. Notice that the Random Walk is imprecise, while the predictions generated by the algorithm in \cite{Kitani2012} suffer from the inability of their motion model to adequately match the speed of the agent.}

@@

	\caption{An illustration of the predictions generated by the various algorithms. Notice that the Random Walk is imprecise, while the predictions generated by the algorithm in \cite{Kitani2012} are unable to match the speed of the agent and choose the wrong direction to follow the agent around the circle.}

@@

%Our data came from the Stanford Drone Dataset in the form of hand annotated bounding boxes around agents (e.g. cars, pedestrians, bicycles).

Note that the implementation of the algorithm in \cite{Kitani2012} required the endpoint of each test trajectory. 
Without this information the implementation of the predictor provided by the authors devolved into a random walk.
Neither our algorithm nor the random walk were provided this information.

The output distributions of the three algorithms were compared using their integrals over the cells of a regular grid over our domain. 
These integrals are used to visualize the distributions in Figures \ref{fig:death-1-2} and \ref{fig:bookstore-1-2}.
%In keeping with our measurement model, the ground truth compared against was a grid that was identically zero except on a bounding box around the measurement at time $t$. 
%The ground truth bounding box at each time instance were set equal to the average bounding box dimension centered at the 
%were the average bounding box dimensions in the training data set. 
Because our predictions all share the same scale, we were able to amalgamate all of the prediction and truth values for all of the simulated agents at a given time step and generate ROC curves. 
Figure \ref{fig:auc_vs_time} shows the Area Under the Curve of these ROC curves versus time.
Our predictor behaves better than any of the others at moderately large $t$
%, where we capture the behavior of the agent without suffering the misplaced confidence observed in Kitani et al.'s predictions. 
%Their encoding of velocity results in the prediction lagging behind the actual observed motion. 
This is despite the algorithm in \cite{Kitani2012} knowing the specific final location of each agent.
%Even given significantly better information, Kitani et al. generates lower quality predictions than our algorithm at all time scales.

\begin{figure}
	\centering
	\includegraphics[width=\linewidth]{./figures/the_results.eps}
	\caption{A comparison of the AUC of the various algorithms. Note that the initial dip in the performance of \cite{Kitani2012} is due to their confidence in their initial estimate.}
	\label{fig:auc_vs_time}
\end{figure}

\begin{table}
	\begin{center}
		\caption{Comparison of runtimes of the various algorithms.}
		\label{tab:time}
		\renewcommand{\arraystretch}{1.5}% Spread rows out...
		\begin{tabular}{||c | c c  c ||} 
			\hline
			& Our Predictor & Random Walk & Kitani et al. \\ [0.5ex] 
			\hline 
			$\frac{\mathrm{time}}{\mathrm{frame}}$ & 0.0169s & 2.1E-7s & 0.0614s \\
			\hline
		\end{tabular}
	\end{center}
\end{table}

The run time per frame for each algorithm was generated using total run time for 400 frames, averaged across several agents and scenes, divided by the number of frames. 
This is shown in Table~\ref{tab:time}. 
Our algorithm implementation leveraged its embarrassing parallelism using a relatively naive Python implementation, which split the computation of frames among 18 cores. 
%Our run times would significantly decrease using an implementation of our algorithm in C that uses a more clever scheme. 
The algorithm in \cite{Kitani2012} was timed with minimal modification using the source code provided by the authors.

%Figure \ref{fig:auc_vs_time} shows that at all time scales our algorithm has better predictive capability than Kitani et. al's. 
%We also run over 3 times faster than their algorithm, at over 60FPS.  
%Figures \ref{fig:death-1-2} and \ref{fig:bookstore-1-2} show the qualitative superiority of our predictions on several scenes.
